\input{settings}
\input{macros}

\title{\LARGE \bf
Synthesizing Stabilization Feedback using Complex Zonotope
}

%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
%         \thanks{*Use the $\backslash$thanks command to put information here}\\
%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
%         University of Twente\\
%         7500 AE Enschede, The Netherlands\\
%         {\tt\small h.kwakernaak@autsubmit.com}}
%         \hspace*{ 0.5 in}
%         \parbox{3 in}{ \centering Pradeep Misra**
%         \thanks{**The footnote marks may be inserted manually}\\
%        Department of Electrical Engineering \\
%         Wright State University\\
%         Dayton, OH 45435, USA\\
%         {\tt\small pmisra@cs.wright.edu}}
%}

\author{Arvind Adimoolam and Thao Dang% <-this % stops a space
\thanks{}% write supporting organization
\thanks{Thao Dang is with the CNRS, and the Verimag Laboratory, Universit{\'e} Grenoble Alpes, France
        {\tt\small thao.dang@univ-grenoble-alpes.fr}}%
\thanks{Arvind Adimoolam is with the Department of Computer Science and Engineering, IIT Kanpur,
        India.
        {\tt\small santosh@cse.iitk.ac.in}}%
}


\begin{document}



\maketitle
\thispagestyle{empty}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We consider the problem of stabilizing a linear sampled data control
system based on information from previous samples, when the current
sample information is unavailable and also the sampling time is
uncertain.  The control structure can account for distributed
components where theres is possible communication loss resulting in
unavailability of state information in sufficient time.  Therefore, we
focus on synthesizing a stabilizing feedback based on previous sample
to increases the robustness of system to uncertainty in sampling time.
However, simply using time evolution to map the feedback based on
current sample to the feedback based on previous sample may not
provide stabilization for large enough uncertainty in sampling period.
Alternatively, we propose a more effective stabilization technique that
employs complex zonotopes generated by eigenvectors of the dynamics to
represent invariant sets, from which the feedback matrix acting on the
previous state sample is derived.  Complex zonotopes are an extension
of real-valued zonotopes to the complex number domain, which has been
previously used to effectively verify stability of sampled data
control systems.  In this paper, we extend the application of complex
zonotopes to control synthesis.  We evaluate our approach on benchmark
examples and demonstrate stabilization on larger ranges of uncertainty
on sampling time periods than the uncertainty ranges proposed in the
benchmarks.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\keywords Controller Synthesis, Sampled Data, Information loss, Complex Zonotope.}

\section{Introduction}~\label{sec:intro}
\input{sections/intro}
%
\subsection{Related Work}
\input{sections/related}
%
\subsection{Notation}
\input{sections/notation}


\section{Problem}~\label{sec:problem}
\input{sections/problem}

\section{Solution}~\label{sec:solution}
\input{sections/solution}

\section{Evaluation}~\label{sec:evaluation}
\input{sections/evaluation}

\section{Conclusion}
\input{sections/conclusion}

\bibliography{ref}



\end{document}
