For convex optimization in our algorithm, we used CVX~\cite{grant2008cvx}, a package for specifying and solving convex programs.
\begin{example}
% We consider a sampled data system taken from~\cite{hetel2013stabilization}, where $A_s = \mymatrix{0 & 1\\ -2 & 0.1}$, $B = \mymatrix{0 \\ 1}$, $A_u = \mymatrix{0 & 0}$, $B_u = 0$ and $F_c = \mymatrix{1 & 0}$.  
Let us consider the system described in Example~\ref{eg:counterintuitive} in Section~\ref{sec:problem}.
\end{example}
Without previous sample based feedback,~\cite{al2015stability} has shown this system is stable for sampling times in $\sqb{0.4,1.888}$, but unstable for $\ub\geq 1.889$.  We want to exponentially stabilize the system for a large $\ub>1.889$, given $\lb = 0.4$ and $\lambda = 0.9999$, using previous sample based feedback at appropriate update time $\rb{\theta+\lb}$.  However, if we set a matching feedback matrix $F_p = F_c\exp\rb{A_c 1.888}$ acting on previous sample at update time $1.888$, where $\theta = 1.488$, the system will be unstable for $\ub\geq 1.898$.    This is because $\R{0.4}\R{1.898} = A_r\exp\rb{0.4 A_c}A_r\exp\rb{0.01 A_c}A_r\exp\rb{1.888 A_c}$ has eigenvalues outside unit complex circle.  So, choosing $F_p$ based on the expected feedback  does not give an increment of more than $0.01$ in the stabilization interval compared to the previous stability interval. 

On the other hand, our algorithm can find a different $F_p$ that does increase the sampling time range of stability to a large value $\ub = 3.42$ as given in the following result.

\emph{Settings}.  $\lb = 0.4$, $K = 2$, $\eta = \epsilon = 0.01$, $\lambda = 0.9999$, $\gamma = 0.6$.

\emph{Result}.  For $\ub = 3.42$, our algorithm found $F_p = \mymatrix{0.1422 &   0.4669  &  0.1417}$ with $\theta = 1.41$ to exponentially stabilize the system.  

\begin{example}
We consider a sampled data system taken from~\cite{hetel2017recent}, where $A_s = \mymatrix{1 & 3\\ 2 & 1}$, $B_s = \mymatrix{1 \\ 0.6}$, $A_u = \mymatrix{0 & 0}$, $B_u = 0$ and $F_c = \mymatrix{-1 & -6}$.  
\end{example}
Without previous sample based feedback, given $\tau_{min} = 0.18$, the system is shown in~\cite{hetel2017recent} to be unstable for $\tau_{max}\geq 0.54$.  Given $\lambda = 0.999$, we want to $\lambda$-exponentially stabilize the system for a large $\tau_{max}> 0.54$. 

\emph{Settings}.  $\lb = 0.18$, $K = 2$, $\eta = \epsilon = 0.01$, $\lambda = 0.999$, $\gamma = 12$.

\emph{Result}.   For $\ub = 0.8$, our algorithm found $F_p = \mymatrix{-10.5819  &  1.7823 &  -2.5906}$ with $\theta = 0.31$ to exponentially stabilize the system.

\begin{example}
We consider a sampled data system taken from~\cite{hetel2013stabilization}, where $A_s = \mymatrix{0 & -3\\ 1.4 & -2.6}$, $B_s = \mymatrix{1 \\ 0.6}$, $A_u = \mymatrix{8.4 -18.6}$, $B_u = 4.6$ and $F_c = \mymatrix{0 & 0}$.  
\end{example}
Without previous sample based feedback, given $\tau_{min} = 0.1$, the system is shown in~\cite{al2015stability} to be unstable for $\tau_{max}\geq 0.515$.  Given $\lambda = 0.99$, we want to $\lambda$-exponentially stabilize the system for a large $\tau_{max}> 0.515$ by finding a suitable $F_p$ and $\theta$.

\emph{Settings}. $\lb = 0.1$, $K = 2$, $\epsilon = \eta = 0.001$, $\lambda = 0.99$, $\gamma = 0.1$.

\emph{Result}.   For $\ub = 0.86$, our algorithm found $F_p = \mymatrix{0.0972 &  -0.0056  &  0.0085}$ with $\theta = 0.38$ to exponentially stabilize the system.

\begin{example}~\label{eg:net}
This example is adapted from the example of a networked platoon of
vehicles given in~\cite{makhlouf2014networked}, where the state space
is $9$-dimensional and the sampled input is $2$-dimensional.  The
matrices of system dynamics are give in Table~\ref{tab:mats}.
%
\end{example}
%
Without previous sample based feedback, given $\tau_{min} = 0.3$, using
complex zonotope we verified exponential stability for $\tau_{max} =
2.35$.  So, given $\lambda = 0.99$, we want to $\lambda$-exponentially
stabilize the system for a larger $\tau_{max}> 2.35$.

\emph{Settings}. $\lb = 0.3$, $K = 2$, $\epsilon = \eta = 0.01$, $\lambda = 0.99$, $\gamma = 12$.


\emph{Result}.   For $\ub = 4.41$, our algorithm found the $F_p$ given in Table~\ref{tab:res-net}
%
with $\theta = 2.05$ to exponentially stabilize the system.
