Sampled data systems are systems where the feedback input is periodically sampled based on information received about the state of the system, typically over a communication network.  They can be used to control distributed components of a system via communication networks.  But communication networks are prone to loss of information, which can result
in subsequent inactuation and instability of a sampled data system.  In the case of information loss,
we may expect to stabilize the system by applying feedback based
on information from previous samples.  However, the sampling time can
be uncertain and time varying in realistic systems, due to which the
problem of finding appropriate stabilizing feedback based on the
previous sample becomes challenging.  

For instance, the expected
feedback at the current time instant can be written as a function of
the previous sample (see Remark~\ref{rem:counterintuitive}).  But
counterintuitively, such feedback may not effectively stabilize the
system since the time at which the future sample information becomes
available is uncertain (\emph{this is explained in
  Example~\ref{eg:counterintuitive}}).  There can be other
feedbacks acting on previous samples which may stabilize the system more robustly, i.e., for
larger ranges of uncertainty in the sampling time.  Earlier research
works~\cite{briat2013convex,hetel2013stabilization} have tackled the
problem of finding stabilizing feedback based on the current sample
when the sampling time is uncertain.  However, to our knowledge, this
problem of stabilizing system based on previous sample information
when the current sample information is missing and the future sampling
time in uncertain, has not been tacked yet.

In this paper, we come up with an algorithm to find the
stabilizing feedback based on previous sample when the current sample
information is missing and the sampling time is uncertain.  To this
end, we find a novel application of a set representation called
\emph{complex zonotope}~\cite{adimoolam2018calculus}.  Complex
zonotope is an extension of real valued zonotopes to complex plane
which has been earlier applied to verify stability of sampled data
systems based on its complex valued
eigenstructure~\cite{adimoolam2016using,adimoolam2017template}.  In
this paper, we extend the application of complex zonotope to
synthesize stabilizing feedback acting on previous sample, given range
of uncertainty in sampling time.  We make use of the possibly complex
valued eigenstructure of the dynamics to find an candidate complex
zonotopic invariant for the system and then synthesize the required
stabilizing feedback acting on the previous sample.

